lfl: Linguistic Fuzzy Logic in \R{} -- Part I

### 2021-02-06 article1.tex

\newenvironment{Schunk}{}{}
\newenvironment{Sinput}{\endgraf\verbatim}{\endverbatim}
\newenvironment{Soutput}{\endgraf\verbatim}{\endverbatim}
\newcommand{\pkg}[1]{\textbf{#1}}
\newcommand{\proglang}[1]{#1}
\newcommand{\code}[1]{\texttt{#1}}

@@

@@

\title{lfl: Linguistic Fuzzy Logic in \R{}}

%% Group authors per affiliation:
\author{Michal Burda\corref{corr}}\ead{Michal.Burda@osu.cz}
\author{Martin \v{S}t\v{e}pni\v{c}ka}
\cortext[corr]{Corresponding author. Tel.: +420 59 709 1450; fax: +420 596 120 478.}
\address{Institute for Research and Applications of Fuzzy Modeling, University of Ostrava, CE~IT4Innovations, 30.~dubna 22, 701 03 Ostrava, Czech Republic}

@@

\michal{jak zvýraznovat název balíku pro R? v templatu JSTATSOFT to bylo tučně, tady taky tak?}

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[width=120mm]{DEE.png}
	\caption{Visual sketch of fuzzy sets representing some particular evaluative linguistic expressions. Specific defuzzification DEE is charted too.}\label{fig_dee}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figure/horizon-1.pdf}
    \caption{Horizons for the atomic expressions \emph{small}, \emph{medium} and \emph{big} in the unilateral trichotomy (\code{ctx3(0, 0.5, 1)})}
    \label{fig:horizon}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figure/lingexpr1-1.pdf}
    \includegraphics{figure/lingexpr2-1.pdf}
    \includegraphics{figure/lingexpr3-1.pdf}
    \caption{All pre-defined linguistic expressions for the unilateral trichotomy context \code{ctx3}}
    \label{fig:lingexpr}
\end{figure}

@@

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics{figure/triangular1-1.pdf}
        \caption{\code{triangular(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics{figure/triangular2-1.pdf}
        \caption{\code{triangular(-Inf, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics{figure/raisedcos1-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics{figure/raisedcos2-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, Inf)}}
    \end{subfigure}
    \caption{Triangular and raised-cosinal functions}
    \label{fig:triangular}
\end{figure}

@@

\begin{figure}
    \centering
    \newsavebox{\largestimage}
    \savebox{\largestimage}{\includegraphics[width=0.4\textwidth]{figure/fcut_plot1-1.pdf}}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \usebox{\largestimage}
        \caption{\code{merge=1}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \raisebox{\dimexpr0.07\ht\largestimage}{%
            \includegraphics[width=0.82\textwidth]{figure/fcut_plot2-1.pdf}}
        \caption{\code{merge=2}}
    \end{subfigure}
    \caption{Results of the \code{fcut} call with \code{breaks=c(1, 3, 5, 7, 9)} and different settings of \code{merge}.}
    \label{fig:fcut}
\end{figure}

>>>>

%\newenvironment{Schunk}{}{}
\newenvironment{Schunk}{\bgroup\linespread{1}}{\egroup}
\newenvironment{Sinput}{\endgraf\verbatim}{\endverbatim}
\newenvironment{Soutput}{\endgraf\verbatim}{\endverbatim}
\newcommand{\pkg}[1]{\textbf{#1}}
\newcommand{\proglang}[1]{#1}
\newcommand{\code}[1]{\texttt{#1}}

@@

\newcommand{\Martin}[1]{{\color{blue} Martin: #1}}

@@

\title{lfl: Linguistic Fuzzy Logic in \R{} -- Part I}

%% Group authors per affiliation:
\author{Michal Burda\corref{corr}}\ead{Michal.Burda@osu.cz}
\author{Martin \v{S}t\v{e}pni\v{c}ka}\ead{Martin.Stepnicka@osu.cz}
\cortext[corr]{Corresponding author. Tel.: +420 59 709 1450; fax: +420 596 120 478.}
\address{Institute for Research and Applications of Fuzzy Modeling, University of Ostrava, CE~IT4Innovations, 30.~dubna 22, 701 03 Ostrava, Czech Republic}

@@

\Martin{Utekly mi obrazky pod reference na konec clanku - nevim proc. \\ Premyslim nad tim delenim clanku na part I a Part II. Mozna pri zkraceni tech prikladu se to vejde do jednoho clanku. Porad totiz tapu, kde tu delici mezeru udelat a jak se v te druhe casti neopakovat. }

@@

\begin{figure}[tbp]
	\centering
	\includegraphics[scale=0.3]{DEE.png}
	\caption{Visual sketch of fuzzy sets representing some particular evaluative linguistic expressions. Specific defuzzification DEE is charted too.}\label{fig_dee}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[scale=0.8]{figure/horizon-1.pdf}
    \caption{Horizons for the atomic expressions \emph{small}, \emph{medium} and \emph{big} in the unilateral trichotomy (\code{ctx3(0, 0.5, 1)})}
    \label{fig:horizon}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[scale=0.59]{figure/lingexpr1-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr2-1.pdf}
    \\
    \includegraphics[scale=0.59]{figure/lingexpr3-1.pdf}
    \caption{All pre-defined linguistic expressions for the unilateral trichotomy context \code{ctx3}}
    \label{fig:lingexpr}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/triangular1-1.pdf}
        \caption{\code{triangular(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/triangular2-1.pdf}
        \caption{\code{triangular(-Inf, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/raisedcos1-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, 1)}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \includegraphics[scale=0.80]{figure/raisedcos2-1.pdf}
        \caption{\code{raisedcosinal(0, 0.5, Inf)}}
    \end{subfigure}
    \caption{Triangular and raised-cosinal functions}
    \label{fig:triangular}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \newsavebox{\largestimage}
    \savebox{\largestimage}{\includegraphics[width=0.4\textwidth]{figure/fcut_plot1-1.pdf}}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \usebox{\largestimage}
        \caption{\code{merge=1}}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \centering
        \raisebox{\dimexpr0.07\ht\largestimage}{%
            \includegraphics[width=0.82\textwidth]{figure/fcut_plot2-1.pdf}}
        \caption{\code{merge=2}}
    \end{subfigure}
    \caption{Results of the \code{fcut} call with \code{breaks=c(1, 3, 5, 7, 9)} and different settings of \code{merge}.}
    \label{fig:fcut}
\end{figure}
